Who does big team science?

### 2024-02-07 manuscript_scopus_unmasked.Rmd
unmasked paper

  Computational reproducibility: All materials and code can be found on our OSF page: MASKED FOR REVIEW or corresponding GitHub archive: MASKED FOR REVIEW. Elsevier has agreed to provide access to determine reproducibility of the code for accessing and summarizing articles, and the reproducible manuscript has been provided for review.

  Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (MASKED FOR REVIEW^[Unfortunately, the way we created these pre-registrations did not allow for complete anonymization required by the journal, this work has been uploaded a deidentified zip file]) but then was updated with access to the Scopus database for a broader picture of BTS projects (MASKED FOR REVIEW).

  Materials: MASKED FOR REVIEW (see uploaded zip file).

  Data: MASKED FOR REVIEW (see uploaded zip file).

  Analysis scripts: MASKED FOR REVIEW (see uploaded zip file).

keywords          : "big team, science, authorship, credit"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : yes
draft             : no
classoption       : "man"
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: inline
bibliography: references.bib
appendix          :
  - "appendix.Rmd"

>>>>

  Computational reproducibility: All materials and code can be found on our OSF page: https://osf.io/cgx6u/ or corresponding GitHub archive: https://github.com/doomlab/big_team_who. Elsevier has agreed to provide access to determine reproducibility of the code for accessing and summarizing articles, and the reproducible manuscript has been provided for review.

  Pre-registration: This manuscript was preregistered with the same conceptual ideas using Google Scholar and ORC-ID databases (https://osf.io/f2dtr) but then was updated with access to the Scopus database for a broader picture of BTS projects (https://osf.io/fheun).

  Materials, Data, Analysis Scripts: All materials and code can be found on our OSF page: https://osf.io/cgx6u/ or corresponding GitHub archive: https://github.com/doomlab/big_team_who.

keywords          : "big team, science, authorship, credit"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
classoption       : "man"
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: inline
bibliography: references.bib
appendix          :
  - "appendix.Rmd"
